To Do List

### 2019-10-22 Papers.Rmd
Add Peakachu
Add Ramirez 2018, TFBSs at TAD boundaries

- Salameh, Tarik J, Xiaotao Wang, Fan Song, Bo Zhang, Sage M. Wright, Chachrit Khunsriraksakul, and Feng Yue. “A Supervised Learning Framework for Chromatin Loop Detection in Genome-Wide Contact Maps.” Preprint. Bioinformatics, August 20, 2019. https://doi.org/10.1101/739698. - Peakachu - loop prediction from Hi-C data using random forest. ChIA-PET and HiChIP provide positive training examples. H3K27ac HiChIP better predicts short-range interactions, CTCF ChIA-PET is better for longer interactions. Each pixel is characterized by 11x11 window, 10Kb resolution data, Gm12878 and K562 cell line. Excels for short-range interactions. Model trained using data from Hi-C performs well in other technologies, Micro-C, DNA SPRITE. Code athttps://github.com/tariks/peakachu, Predicted loops for 56 cell/tissue types are available athttp://promoter.bx.psu.edu/hi-c/publications.html

>>>>

- Salameh, Tarik J, Xiaotao Wang, Fan Song, Bo Zhang, Sage M. Wright, Chachrit Khunsriraksakul, and Feng Yue. “A Supervised Learning Framework for Chromatin Loop Detection in Genome-Wide Contact Maps.” Preprint. Bioinformatics, August 20, 2019. https://doi.org/10.1101/739698. - Peakachu - loop prediction from Hi-C data using random forest. ChIA-PET and HiChIP provide positive training examples. H3K27ac HiChIP better predicts short-range interactions, CTCF ChIA-PET is better for longer interactions. Each pixel is characterized by 11x11 window, 10Kb resolution data, Gm12878 and K562 cell line. Excels for short-range interactions. Model trained using data from Hi-C performs well in other technologies, Micro-C, DNA SPRITE. Code athttps://github.com/tariks/peakachu, Predicted loops for 56 cell/tissue types are available at http://promoter.bx.psu.edu/hi-c/publications.html

- Ramírez, Fidel, Vivek Bhardwaj, Laura Arrigoni, Kin Chung Lam, Björn A. Grüning, José Villaveces, Bianca Habermann, Asifa Akhtar, and Thomas Manke. “High-Resolution TADs Reveal DNA Sequences Underlying Genome Organization in Flies.” Nature Communications 9, no. 1 (December 2018). https://doi.org/10.1038/s41467-017-02525-w. - TFBSs enriched at and can predict TAD boundaries in Drosophila. Eight motifs are enriched, CTCF to a lesser extent. Classification of TAD boundaries into active/inactive, promoters/non-promoters, correlation with gene expression. Most promoter-boundaries are marked by divergent promoters, genes at them have higher expression and lower variability. Motif combination is predictive of boundary strength. TAD boundary prediction (Linear, Logistic, GBM, RF) identifies open chromatin as an important feature.
